---
title: "linear model from Web"
author: "Aylin Torres"
date: "10/03/24"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
model.1=lm(SIMS~ARM, data=data)
abline(model.1)
```

 This scatterplot shows simulated strength increases (SIMS) increase ARM streght increased


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
correlation = 0.69 shows moderate positive correlation between SIMS score and arm strength


### Inferential  (Build model.1)

```{r}
summary.lm(model.1)
```

model.1 shows that the intercept and coefficient of ARM are both significantly different from 0.

#### Predict at target point

```{r}
targtpoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.1, targtpoint, interval = 'prediction') 
print(predictInt)
```

at ARM=88 GRIP=94, the predicted SIMS score is 0.706. 95% confidence interval for that score is SIMS between -1.73 and 3.19

#### scatterplot with model fit
  
```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~GRIP, data=data)
abline(model.2)
```
This scatterplot shows simulated strength increases (SIMS) increase GRIP streght increased


## Model 2 SIM~GRIP


### Now add in scatterplot


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
correlation = 0.64 shows moderate positive correlation between SIMS score and arm strength

### Inferential  (Build model.2)

```{r}
summary.lm(model.2)
```
model.2 shows that the intercept -4.80 and coefficent 0.45 of GRIP are both significantly different from 0.

#### predict model.2 at target point

```{r}
targtpoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.2, targtpoint, interval = 'prediction') 
print(predictInt)
```
at ARM=88 GRIP=94, the predicted SIMS score is -0.53 95% confidence interval for that score is SIMS between -3.10 and 2.03


#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 =lm(SIMS~ARM+GRIP, data=data)
summary(model.3)
```
model.3 shows that the intercept 5.43 and coefficient 0.037 of ARM and 0.24 of GRIP.The p-value for both is lower than 0.05


### Numerical results (cor)

```{r}
cor(data)
```
SIMS  corrolates with GRip and ARM with these values.
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point

```{r}
predict(model.3, targtpoint, interval='prediction')
```
  

## Comparing nested models ANOVA Test


### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova_result <- anova(model.1, model.3)
print(anova_result)
```
Model.2 is  much better than model one because the p-value in comparison is less than 0.05


```{r}
anova_result <- anova(model.2, model.3)
print(anova_result)
```

Model.3